\mytitle

### 2022-01-06 paper/noms-short-paper.tex
Camera readied!

\title{\mytitle}
\author{Kyle~A.~Simpson~\orcidlink{0000-0001-8068-9909}, Dimitrios~P.~Pezaros~\orcidlink{0000-0003-0939-378X}\\\emph{University of Glasgow}, Glasgow, Scotland\\\email{k.simpson.1@research.gla.ac.uk}, \email{Dimitrios.Pezaros@Glasgow.ac.uk}}

\begin{document}

@@

@@

%\vspace{-1em}
\section{Introduction}
\begin{figure}
	\centering
	\includegraphics[keepaspectratio, width=0.65\linewidth]{figures/arch-with-p4}
	\caption{\approachshort{} brings low-latency, online reinforcement learning directly to the dataplane. SoC- and NetFPGA-based SmartNIC devices expose spare compute---making in-situ, asynchronous processing and learning possible alongside P4 dataplanes. Classical RL policy methods are the key to making this feasible.\label{fig:netro-arch}}
\end{figure}
Automatic network optimisation, control, and defence are at last becoming commonplace.
Adaptive techniques such as \emph{reinforcement learning} (RL) have led the charge in data-driven networking, enhancing automatic traffic optimisation~\parencite{DBLP:conf/sigcomm/ChenL0L18,DBLP:conf/sigcomm/MaoNA17}, congestion control~\parencite{DBLP:journals/corr/abs-1910-04054}, adaptive routing~\parencite{DBLP:conf/hotnets/ValadarskySST17,DBLP:conf/conext/GiladSGRS20}, resource management~\parencite{DBLP:conf/hotnets/MaoAMK16}, and packet classification~\parencite{DBLP:conf/sigcomm/LiangZJS19}.
In RL methods, every change and its effects improve future decisions.

@@

@@

@@

\begin{figure}
	\centering
	\includegraphics[keepaspectratio, width=0.65\linewidth]{figures/coop}
	\caption{\approachshort{} scales to fit device capacity according to either latency or throughput needs---\Coopfw{} is the optimal online design. A single \emph{controller} delegates RL inference and updates to many \emph{minions}, who complete independent subtasks.\label{fig:single-and-parallel:parallel}}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\resizebox{\resultplotwidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-core}
	}
	\caption{
		\Coopfw{}'s online learning performance improves with additional cores. This requires \num{8} workers to offer greater online throughput than single-threaded in-NIC RL. Sharper performance increases occur when a new physical core is added (\numrange{7}{8}) or the scheduler works around a bottleneck (\numrange{13}{14}).\label{fig:vary-core}}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\resizebox{\resultplotwidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-work}
	}
	\caption{\Coopfw{} processes updates faster than \Indfw{}---thus has higher online performance---on almost all policy sizes. Lower bit depths are effective on simple policies. State-action latency scales similarly.\label{fig:vary-work}}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\resizebox{1.0\linewidth}{!}{
%			\includegraphics{../plots/build/stress/heat-latency-median}
			\includegraphics{../plots/build/stress/heat-latency-two-9-rel}
%			\includegraphics{../plots/build/stress/heat-latency-two-9-perc}
		}
		\caption{Deviations in \nth{99} percentile cross-traffic RTTs.\label{fig:dataplane-heat}}
	\end{subfigure}
	\hspace{0.05\linewidth}
		\begin{subfigure}{0.45\linewidth}
		\resizebox{1.0\linewidth}{!}{
			\includegraphics{../plots/build/stress/histo-128B-0-3-trim}
		}
		\caption{RTT distribution for \SI{128}{\byte} packets at \numlist{0;3000} RL actions/s.\label{fig:dataplane-example}}
	\end{subfigure}
	\caption{Effects on tail latency of cross-traffic caused by off-path RL compute. Statistically significant increases in population latency are concentrated on smaller packet sizes, and are typically sub-\SI{78}{\nano\second}.\label{fig:dataplane-coop}}
\end{figure}

>>>>

%\usepackage[T1]{fontenc}

\title{\mytitle}
\author{Kyle~A.~Simpson~{\orcidlink{0000-0001-8068-9909}~\scriptsize[0000-0001-8068-9909]}, Dimitrios~P.~Pezaros~{\orcidlink{0000-0003-0939-378X}~\scriptsize[0000-0003-0939-378X]}\\\emph{University of Glasgow}, Glasgow, Scotland\\\email{k.simpson.1@research.gla.ac.uk}, \email{Dimitrios.Pezaros@Glasgow.ac.uk}}

%\IEEEpubid{\makebox[\columnwidth]{978-1-6654-0601-7/22\/\$31.00 ~\copyright~2022 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}
\begin{document}

@@

%\IEEEoverridecommandlockouts \IEEEpubid{\makebox[\columnwidth]{978-1-6654-0601-7/22\/\$31.00 ~\copyright~2022 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

@@

%\vspace{-1em}
\section{Introduction}
Automatic network optimisation, control, and defence are at last becoming commonplace.
Adaptive techniques such as \emph{reinforcement learning} (RL) have led the charge in data-driven networking, enhancing automatic traffic optimisation~\parencite{DBLP:conf/sigcomm/ChenL0L18,DBLP:conf/sigcomm/MaoNA17}, congestion control~\parencite{DBLP:journals/corr/abs-1910-04054}, adaptive routing~\parencite{DBLP:conf/hotnets/ValadarskySST17,DBLP:conf/conext/GiladSGRS20}, resource management~\parencite{DBLP:conf/hotnets/MaoAMK16}, and packet classification~\parencite{DBLP:conf/sigcomm/LiangZJS19}.
In RL methods, every change and its effects improve future decisions.

@@

%\vspace{-0.3em}

@@

\begin{figure}[h]
	\centering
	\includegraphics[keepaspectratio, width=0.65\linewidth]{figures/arch-with-p4}
	\vspace{-0.5em}
	\caption{\approachshort{} brings low-latency, online reinforcement learning directly to the dataplane. SoC- and NetFPGA-based SmartNIC devices expose spare compute---making in-situ, asynchronous processing and learning possible alongside P4 dataplanes. Classical RL policy methods are the key to making this feasible.\label{fig:netro-arch}}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[keepaspectratio, width=0.69\linewidth]{figures/coop-stretch}
	\vspace{-0.5em}
	\caption{\approachshort{} scales to fit device capacity according to either latency or throughput needs---\Coopfw{} is the optimal online design. A single \emph{controller} delegates RL inference and updates to many \emph{minions}, who complete independent subtasks.\label{fig:single-and-parallel:parallel}}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\resizebox{\resultplotwidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-core-bigtext}
	}
\vspace{-0.5em}
	\caption{
		\Coopfw{}'s online learning performance improves with additional cores. This requires \num{8} workers to offer greater online throughput than single-threaded in-NIC RL. Sharper performance increases occur when a new physical core is added (\numrange{7}{8}) or the scheduler works around a bottleneck (\numrange{13}{14}).\label{fig:vary-core}}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\resizebox{\resultplotwidth}{!}{
		\includegraphics{../plots/build/rl-perf-tester/vary-work-bigtext}
	}
\vspace{-0.5em}
	\caption{\Coopfw{} processes updates faster than \Indfw{}---thus has higher online performance---on almost all policy sizes. Lower bit depths are effective on simple policies. State-action latency scales similarly.\label{fig:vary-work}}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.525\linewidth}
		\resizebox{1.0\linewidth}{!}{
%			\includegraphics{../plots/build/stress/heat-latency-median}
			\includegraphics{../plots/build/stress/heat-latency-two-9-rel-bigtext}
%			\includegraphics{../plots/build/stress/heat-latency-two-9-perc}
		}
		\vspace{-1.75em}
		\caption{\nth{99} \%tile cross-traffic RTT changes.\label{fig:dataplane-heat}}
	\end{subfigure}
%	\hspace{0.05\linewidth}
		\begin{subfigure}{0.46\linewidth}
		\resizebox{1.0\linewidth}{!}{
			\includegraphics{../plots/build/stress/histo-128B-0-3-trim-div}
		}
		\caption{RTT distribution for \SI{128}{\byte} packets at \numlist{0;3000} actions/s.\label{fig:dataplane-example}}
	\end{subfigure}
	\caption{Effects on tail latency of cross-traffic caused by off-path RL compute. Statistically significant increases in population latency are concentrated on smaller packet sizes, and are typically sub-\SI{78}{\nano\second}.\label{fig:dataplane-coop}}
\end{figure}
